\section{Data samples}

We use the full Run 1 sample from Stripping 21 with Reco14, consisting of 3 $\invfb$ of data, collected in the years 2011 and 2012 at a center of mass energies of 7 $\tev$ and 8 $\tev$, respectively. 
The selected $\Bs$-candidates are required to pass the L0 Hadron trigger on signal (TOS) or the L0 Global trigger independent of signal (TIS).\newline 
Events that pass the L0 stage are further required to pass the HLT1 TrackAllL0 trigger on signal (TOS). \newline
All remaining candidates have to pass either the 2, 3 or 4-body topological trigger (TOS) of the HLT2 stage. More information on the HLT lines used in this analysis is given in Appendix \ref{sec: trigger}.\newline
For the presented analysis the B02DKPiPiD2HHHPIDBeauty2CharmLine is used to preselect signal $\Bs\to\Ds\kaon\pion\pion$ candidates and the B02DPiPiPiD2HHHPIDBeauty2CharmLine is used for the selection of $\Bs\to\Ds\pion\pion\pion$ candidates. Both stripping lines employ the same selection cuts for the $\Bs$, $\Ds$, $\kaon$ and $\pion$ candidates. A summary of those cuts can be found in Table \ref{table:StrippingCuts}. 
In this table and throughout the note, we abbreviate $\Bs\to\Ds X_{s}(\to\kaon\pion\pion)$ and $\Bs\to\Ds X_{d}(\to\pion\pion\pion)$, identifying $X_{s}\to\kaon\pion\pion$ and 
$X_{d}\to\pion\pion\pion$ as the various resonances through which the decays proceed. The following text describes variables that might be ambiguous and/or cuts which benefits are not straight forward.\newline
In Table \ref{table:StrippingCuts}, DOCA is the abbreviation for distance of closest approach. This variable is used to ensure that all $\Ds$ and $X_{s,d}$ daughters originate from the same vertex.      
The minimal flight distance (FD) $\chi^{2}$ is a measure on how likely a particle traveled some distance before it decayed. A cut on this variable is employed to reject prompt background for $\Ds$ and $X_{s,d}$ candidates.
DIRA is the abbreviation for the cosine of the angle $\theta$ between the hadron's flight direction $\vec{x}$ and it's corresponding momentum vector $\vec{\ptot}$, $\cos{\theta_{\vec{x} -\vec{\ptot}}}$. 
For signal hadrons this variable is expected to be very close to one, while it can be arbitrary distributed for background. 

\begin{table}[h]
\centering
 \begin{tabular}{l l}
Variable & Stripping Cut\\
  \hline
Track $\chi^{2}$/nDoF & $<$ 3\\
Track $\ptot$ & $>$ 1000 $\mevc$\\
Track $\pt$ & $>$ 100 $\mevc$\\
Track IP $\chi^{2}$ & $>$ 4\\
$\Ds$ Daughter $\pt$ & $\Sigma_{i=1}^{3} p_{i} > 1800 \mevc$\\
$\Ds$ Daughter DOCA & $<0.5$ $\mm$\\
$\Ds$ mass $m_{\Ds}$  & within $\pm$ 40 $\mevcc$ of PDG value\\
$\Ds$ Vertex $\chi^{2}$/nDoF & $<$ 10\\
$\Ds$ min FD $\chi^{2}$ & $>$ 36\\
$\Ds$ FD $\chi^{2}$ $>$ 2 to any PV\\
%($Z_{\Ds\mbox{ }decay}$ - $Z_{\Bs\mbox{ }decay}$) & $>$ 0 $\mm$\\
$X_{d}$ Daughter $\pt$ & $>$ 2 $\gevc$\\
$X_{s,d}$ Daughter DOCA & $<0.4$ $\mm$\\
$X_{s,d}$ Daughter $\pt$ & $\Sigma_{i=1}^{3} p_{t,i} > 1250 \mevc$\\
$X_{s,d}$ Vertex $\chi^{2}$/nDoF & $<$ 8\\
$X_{s,d}$ min FD $\chi^{2}$/nDoF & $>$ 16\\
$X_{s,d}$ DIRA & $>$ 0.98\\
$X_{s,d}$ $\Delta\rho$ (vertex displacement perpendicular to z-axis) & $>$ 0.1 $\mm$\\
$X_{s,d}$ $\Delta Z$ (vertex displacement along z-axis) & $>$ 2.0 $\mm$\\
$\Bs$ DIRA & $>$ 0.98\\
$\Bs$ min IP $\chi^{2}$ & $<$ 25\\
$\Bs$ Vertex $\chi^{2}$/nDoF & $<$ 10\\
$\Bs$ $\tauBs$ & $>$ 0.2 $\ps$\\
$\kaon$ \dllkpi & $>$ -5\\
$\pion$ \dllkpi & $<$ 10\\
\end{tabular}
\caption{Summary of the stripping selections for $\Bs\to\Ds\kaon\pion\pion$ decays.}
\label{table:StrippingCuts}
\end{table}
